---
graphics: yes
name: Anthony
surname: Schmidt
headcolor: 01416f
#qualifications: 
position: "Data Viz Researcher | PhD Student"
#address: ""
#phone: ""
www: anthonyschmidt.co
email: "aschmi11@utk.edu"
twitter: anthonyteacher
github: acircleda
aboutme:
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "../csl/apa-cv.csl"
nocite: "@*"
knit: bookdown::render_book
# bibliography_anthony_pub: "../bib/anthony_pub.bib"
# bibliography_anthony_reviews: "../bib/anthony_reviews.bib"
# bibliography_anthony_tech: "../bib/anthony_techreports.bib"
# bibliography_anthony_other: "../bib/anthony_other.bib"
# bibliography_anthony_conf_intl: "../bib/anthony_conf_intl.bib"
# bibliography_anthony_conf_regional: "../bib/anthony_conf_regional.bib"
# bibliography_anthony_conf_posters: "../bib/anthony_conf_posters.bib"
# bibliography_anthony_conf_talks: "../bib/anthony_conf_talks.bib"
# bibliography_anthony_conf_invited: "../bib/anthony_conf_invited.bib"
# bibliography_anthony_conf_workshops: "../bib/anthony_conf_workshops.bib"
header-includes:
  - \usepackage{colortbl}
  - \arrayrulecolor{white}
  - \usepackage{caption}
  - \hypersetup{colorlinks=true, linkcolor=01416f, filecolor=01416f, urlcolor=01416f}
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)


library(RefManageR)
RefManageR::BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           sorting = "ydnt",
           cite.style = "alphabetic",
           style = "markdown",
#           hyperlink = FALSE,
           dashed = FALSE)

library(vitae)
library(tidyverse)
library(gsheet)
library(gt)
```

<!--chapter:end:index.Rmd-->

# Education

```{r education}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1760172285") %>%
  tidyr::fill(-why) %>%
  vitae::detailed_entries(what = Degree,
                          when = Year,
                          where = Institution, 
                          with = Location
                          )
```

<!--chapter:end:education-hyndman.Rmd-->

# Professional Appointments

```{r working-experience}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=161085706") %>%
tidyr::fill(-why) %>%
  vitae::detailed_entries(what = title,
                          when = date,
                          where = institution,
                          why = why,
                          .protect = F)
```

<!--chapter:end:working_exp_detailed-hyndman.Rmd-->

# Publications

## Peer Reviewed Journal Articles

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_pub}
:::
\endgroup

## Pre-Prints and Unpublished Manuscripts

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1558956454") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> preprints
  cat(paste(preprints), sep = '\n\n')

```


\endgroup


## Book Reviews

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_anthony_reviews}
:::
\endgroup

## Technical Reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- BibLaTeX Method (currently not working) -->
<!-- ::: {#refs_anthony_tech} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1473597883") %>%
  select(markdown) %>%
  slice(-1:-6) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> tr
  cat(paste(tr), sep = '\n\n')

```

\endgroup

# Conference Papers and Presentations

## International/National Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_intl} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "intl") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-2) %>%
  pull(markdown) -> intl
  cat(paste(intl), sep = '\n\n')

```

\endgroup

## Regional Conferences

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_regional} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "regional") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-4, -5) %>%
  pull(markdown) -> regional
  cat(paste(regional), sep = '\n\n')

```

\endgroup

## Poster Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<!-- ::: {#refs_anthony_conf_posters} -->
<!-- ::: -->

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=318960497") %>%
  filter(category == "poster") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  slice(-3) %>%
  pull(markdown) -> poster
  cat(paste(poster), sep = '\n\n')

```

# Software

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

```{r results='asis'}
gsheet2tbl("https://docs.google.com/spreadsheets/d/1qbMpXHXm41q69prUVjpQFfP_mMXjORNxFP_IbAoCuKo/edit#gid=1692561333") %>%
  select(markdown) %>%
  mutate(markdown = str_replace_all(markdown, "\\{|\\}", ""),
         markdown = str_replace_all(markdown, "Schmidt, A.", "**Schmidt, A.**")) %>%
  pull(markdown) -> software
  cat(paste(software), sep = '\n\n')

```


\endgroup

<!--chapter:end:publication.Rmd-->

# Current Memberships

American Educational Research Association; American Statistical Society; Roundtable of Sustainable Academic Travel; Association for the Advancement of Sustainability in Higher Education

\

<!--chapter:end:membership.Rmd-->

